---
title: "Video Games Dashboard"
resource_files:
- Video_Game_Sales_as_of_Jan_2017.csv
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    source_code: embed
    theme: simplex
---
```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(plotly)
library(shiny)
library(shinydashboard)
library(rgl)
library(plot3D)
```
```{r global, include=FALSE}
data=read.csv("datavizdata.csv")
```
Data View
===
Column {.sidebar}
---
```{r}
selectInput("GENREVIEW", h3("Genre Filter :"), 
            choices = c(as.character(unique(data$Genre))),
            selected = "Action")
selectInput("PLATFORMVIEW", h3("Platform Filter :"), 
            choices = c(as.character(unique(data$Platform))),
            selected = "NES")
```
Introduction.

Video Games has slowly risen to the title of one of the main branches of the entertainment industry.

Our group decided to investigate this area to look for exciting correlations and trends in this exciting industry. The purpose of this project is to find a pattern and correlation between ratings of the games, popularity, platforms, genres, and developers. We wanted to compare and analyze the market's behavior and understand the scope of the industry as a whole.

Our main objectives and what we wanted to study with this dataset in particular include: 

- Filtering the games by genre and platform to find out what platform had the most games of each genre. 
- Total Game Sales by genre over the years to find out how each genre fair against each other. 
- Comparing Sales Numbers across different regions. 
- Comparing critics and user scores.

Dashboard by Aloysius,Varun,Kartik and Vishvesh.

Row
---
### Data View
```{r}
renderTable({
  data[,c(1:10)] %>%
    filter(Genre==input$GENREVIEW) %>% 
    filter(Platform==input$PLATFORMVIEW) %>%
    head(20)
  })
```

Charts
===
Column {.sidebar}
---
```{r}
selectInput("GENRE", h3("Genre Filter :"), 
            choices = c(as.character(unique(data$Genre))),
            selected = "Action")
```

Coloumn
---
### Total Global Sales Line Plot by Genre

```{r}
renderPlotly({
data %>%
  group_by(Year, Genre) %>%
  summarise(Total_Global_Sales = sum(Global_Sales),.groups = 'keep') %>%
  filter(Genre==input$GENRE) %>%
  data.frame() %>% 
  plot_ly(x = ~Year, 
          y = ~Total_Global_Sales,
          type = "scatter",
          mode = "lines+markers")
})
```

### Count Video Games Genre
```{r}
data %>%
  group_by(Genre) %>%
  summarise(Count = n()) %>%
  plot_ly(x = ~Genre,
          y = ~Count,
          type = "bar")
```
Scatter plot and Correlation plot
===
Column {.sidebar}
---
```{r}
selectInput("XA", h3("Select X axis :"), 
            choices = c("NA_Sales", "EU_Sales", "JP_Sales", "Other_Sales", "Global_Sales"),
            selected = "NA_Sales")
selectInput("YA", h3("Select Y axis :"),
            choices = c("NA_Sales", "EU_Sales", "JP_Sales", "Other_Sales", "Global_Sales"),
            selected = "NA_Sales")
```
Row
---
### Scatter plot
```{r}
renderPlotly({
  data %>%
  plot_ly(x = data[,c(input$XA)],
          y = data[,c(input$YA)])
  })
```


### Correlation Plot
```{r}
data[, c("NA_Sales", "EU_Sales", "JP_Sales", "Other_Sales", "Global_Sales")] %>%
  cor(method = "pearson") %>%
  corrplot::corrplot(addCoef.col = "white")
```

----

3D-Plots
===
Row
---

### 3D Line and Markers Plot
```{r}
fig <- plot_ly(data, x = ~Critic_Score, y = ~User_Score, z = ~User_Count, type = 'scatter3d', mode = 'lines+markers', line = list(width = 3, color = ~Year, colorscale = 'Viridis'),
               marker = list(size = 3.5, color = ~Year,  colorscale = 'Greens', cmin = -20, cmax = 50))
fig
```

---
### 3D Bubble Plot
```{r}
colors <- c('#4AC6B7', '#1972A4', '#965F8A', '#FF7070', '#C61951','Red')

fig <- plot_ly(data, x = ~Global_Sales, y = ~Other_Sales, z = ~User_Count, color = ~Platform, size = ~User_Count, colors = colors,
               marker = list(symbol = 'circle', sizemode = 'diameter'), sizes = c(5, 150),
               text = ~paste('Name:', Name, '<br>Other_Sales:', Other_Sales, '<br>Global_Sales:', Global_Sales,
                             '<br>User_Count', User_Count))
fig <- fig %>% layout(title = '..',
                      scene = list(xaxis = list(title = 'Global_Sales',
                                                gridcolor = 'rgb(255, 255, 255)',
                                                #range=c(1,2),
                                               
                                                type = 'log',
                                                zerolinewidth = 1,
                                                ticklen = 5,
                                                gridwidth = 2),
                                   yaxis = list(title = 'Other_Sales',
                                                gridcolor = 'rgb(255, 255, 255)',
                                                #range=c(1,5),
                                                
                                                zerolinewidth = 1,
                                                ticklen = 5,
                                                gridwith = 2),
                                   zaxis = list(title = 'User_Count',
                                                gridcolor = 'rgb(255, 255, 255)',
                                                #range=c(1000,10000),
                                                type = 'log',
                                                zerolinewidth = 1,
                                                ticklen = 5,
                                                gridwith = 2)),
                      paper_bgcolor = 'rgb(243, 243, 243)',
                      plot_bgcolor = 'rgb(243, 243, 243)')

fig
```
